\documentclass[sigconf]{acmart}

\usepackage{booktabs} % For formal tables
\input{config/localstyle}

% Copyright
\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
\acmDOI{}

% ISBN
\acmISBN{}

%Conference
\acmConference[DAC'2018]{}{May 2018}{San Francisco, CA, US} 
\acmYear{}
\copyrightyear{}


\acmArticle{}
\acmPrice{}

\begin{document}
\title{An Energy Behavior Supporting Simulator for Nonvolatile Processor Based Self-powered System.}

\begin{comment}
\titlenote{Produces the permission block, and
  copyright information}
\subtitle{Extended Abstract}
\subtitlenote{The full version of the author's guide is available as
  \texttt{acmart.pdf} document}
\end{comment}

\begin{comment}
\author{Ben Trovato}
\authornote{Dr.~Trovato insisted his name be first.}
\orcid{1234-5678-9012}
\affiliation{%
  \institution{Institute for Clarity in Documentation}
  \streetaddress{P.O. Box 1212}
  \city{Dublin} 
  \state{Ohio} 
  \postcode{43017-6221}
}
\email{trovato@corporation.com}
\end{comment}

% The default list of authors is too long for headers.
%\renewcommand{\shortauthors}{B. Trovato et al.}

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
%
Battery-less devices and energy harvesting techniques are more and more attractive in today's IoT area. However, the intermittent and low-intensity ambient power sources cause insecure quality of service (QoS) of these self-powered IoT applications, which makes it essential to pre-simulate the QoS of an self-powered system and its energy managing strategy under various power conditions. Unfortunately, existing simulator lacks of supports on peripherals in a self-powered system and requires great efforts to implement the hardware-based energy managing schemes, such as NVP, DVFS and near-threshold designs. 

This paper proposes EBeSS, an system-level simulator based on GEM5, supporting easy-configurable energy managing strategies on both processor and peripherals. EBeSS develops a configurable simulation object, \textbf{virtual device}, to support the functional and energy-related behaviors of peripherals, and \textbf{energy message handling framework} to support configured energy managing strategies. A real hardware prototype validates that the error of EBeSS is less that xx\%. And a self-powered system design flow is given to reveal the potential of EBeSS on exploring the design space of parameters of a self-powered system (such as capacitor and energy managing scheme) with optimal performance.

\end{abstract}

\maketitle

\input{source/intro}
\input{source/tech}
\input{source/valid}
\input{source/exp}
\input{source/sum}

\bibliographystyle{ACM-Reference-Format}
\bibliography{references} 

\end{document}
